Unsupervised Learning for Identifying Events in Active Target Experiments

### 2020-07-10 doc/Manuscript/article.tex
Updates from Overleaf

As an alternative to relying on a pre-trained model, we also consider the MIXAE algorithm \cite{Zhang}, a bespoke end-to-end clustering model which is specifically trained on the AT-TPC data.

@@

It is also interesting to compare and contrast the clustering results from the MIXAE model with those of the VGG16$+$K-means. In particular, the discrepancy in stability is worth noting. While the top performing MIXAE runs outperform the K-means approach, its reliability suffers. However, the high performance achieved shines a light on valuable potential research into more bespoke models for unsupervised track identification.

>>>>

As an alternative to relying on a pre-trained model, we also consider the MIXAE algorithm \cite{Zhang}, which is an end-to-end clustering model specifically trained on the AT-TPC data.

@@

It is also interesting to compare and contrast the clustering results from the MIXAE model with those of the VGG16$+$K-means. In particular, the discrepancy in stability is worth noting. While the top performing MIXAE runs outperform the K-means approach, its reliability suffers. However, the high performance achieved shines a light on valuable potential research into more tailored models for unsupervised track identification.
